Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
Architecture.

\cite{pt}

@@

>>>>

The components of the system are shown in Figure~\ref{fig:architecture}.
The three parts that are new in our system are:
\begin{enumerate}
\item The client program \meekclient.
Using the pluggable transports protocol, tor treats \meekclient\ as a SOCKS proxy.
When \meekclient\ receives data from tor, it bundles it up in an HTTP POST
request and sends it to the web app,
using HTTPS to hide the contents and the domain fronting trick to hide the true destination.
Downstream data are returned in HTTP responses, which \meekclient\ decodes and sends back to tor.
\item The ``reflector'' web app, running on App Engine.
Its domain name \mbox{meek-reflect.appspot.com} is protected by domain fronting.
It is called a reflector because it doesn't do anything intelligent:
it merely copies the HTTP requests it receives and forwards them
to \meekserver\ running on the Tor bridge.
\item The server program \meekserver, which acts as an HTTP server.
It receives reflected requests from the web app, decodes their bodies,
and forwards the contents to an instance of tor running on the same host.
If there is anything pending to be sent back to the client,
\meekserver\ sends it along with its HTTP response.
\meekserver\ also takes care of stringing together multiple HTTP requests
into one logical stream and multiplexing multiple concurrent connections,
both using the technique of session IDs described in this section.
\end{enumerate}

@@

The main technical challenge in making this system work
is in encoding a TCP stream as a sequence of HTTP requests and responses.
\meekserver\ handles many clients at once, and their data streams
are split across multiple HTTP transactions.
In TCP, different streams are distinguished by their
(source~IP, source port, dest~IP, dest~port) tuple,
but we cannot do that because streams are split across multiple TCP sessions.
Rather, each instance of \meekclient\ generates at startup a random 32-byte
session ID, which is sent along with its requests in a special
X-Session-ID HTTP header.
\meekserver, when it sees a particular session ID for the first time,
opens up a new connection to the local tor process,
and stores the session ID in a cache. Subsequent requests with the
same session ID will reuse the same tor connection.
Entries are removed from the cache after a period of inactivity.

HTTP is fundamentally a pull-based protocol.
There is no way for the server to send data to the client without
the client first making a request.
The same applies to meek: when \meekserver\ has data to send back to
a client with a particular session ID, it cannot do so until it
receives a request from that client.
For this reason, \meekclient\ polls the server,
sending an empty request if necessary, every so often.
The polling interval starts short (100~ms) and grows exponentially
up to a maximum of 5~s.
Alternative techniques for push-like behavior,
such as HTTP long polling,
don't work well with App Engine,
because App Engine requires requests to finish within 60 seconds.

We implemented meek as a pluggable transport~\cite{pt} for Tor.
Although it is possible to use the system with proxies other than Tor,
using Tor has some attractive features.
The pluggable transports infrastructure makes it relatively easy to prototype
a circumvention technique and connect it to a global proxy network.
We can treat confidentiality and integrity of tunnelled communication
as a problem solved by Tor, which we don't need to solve separately.
Tor's extra proxy hops mean that the HTTP reflector (App Engine)
and the entry bridge do not have to be trusted.
